Circumpolar variations in the chaotic nature of Southern Ocean eddy dynamics

### 2022-01-06 paper/main.tex
fixing line numbers
final minor edits to second draft

\documentclass{agujournal2019}

\graphicspath{ {figures/} }
\usepackage{lineno,layouts,microtype}

@@

\linenumbers

@@

\newcommand{\mathbfit}[1]{\textbf{\textit{\textsf{#1}}}}
\usepackage{amsfonts, amssymb, amsmath}
\usepackage[labelfont=bf]{caption}

@@

\authors{
Andrew McC. Hogg\affil{1}, Thierry Penduff\affil{2}, Sally E. Close\affil{2}, William K. Dewar\affil{3},\\Navid C. Constantinou\affil{1}, \quad and\quad Josu{\'e} Mart{\'i}nez Moreno\affil{1}
}

@@

\begin{keypoints}
\item Variability in the Southern Ocean eddy field is dominated by chaotic, rather than forced, processes.
\item The forced component of the eddy kinetic energy variance is significantly correlated with the local wind stress input.
\item The eddy field lags the wind stress, with two clear timescales emerging: one at $\sim$6 months, which we attribute to baroclinic instability, and one at 2-3 years, which we attribute to the delayed effect of topographic steering.
\end{keypoints}

\begin{abstract}
Circulation in the Southern Ocean is unique.
The strong wind stress forcing and buoyancy fluxes, in concert with the lack of continental boundaries, conspire to drive the Antarctic Circumpolar Current replete with an intense eddy field.
The effect of Southern Ocean eddies on the ocean circulation is significant -- they modulate the momentum balance of the zonal flow, and the meridional transport of tracers and mass.
The strength of the eddy field is controlled by a combination of forcing (primarily thought to be wind stress) and intrinsic, or chaotic, variability associated with the turbulent flow field itself.
Here, we present results from an eddy-permitting ensemble of ocean model simulations to investigate the relative contribution of forcing and intrinsic processes in governing the variability of Southern Ocean eddy kinetic energy.
We find that chaotic processes dominate the eddy field, even on longer timescales.
Where correlations between the forcing and the eddy field exist, these interactions are dominated by two distinct timescales -- a fast baroclinic instability response; and a multi-year process owing to feedback between bathymetry and the mean flow.
These results suggest that understanding Southern Ocean eddy dynamics and its larger-scale impacts requires an ensemble approach to eliminate intrinsic variability, and therefore may not yield robust conclusions from observations alone.

\noindent \textbf{Plain language summary} \\
\noindent The Southern Ocean is the most turbulent part of the world's oceans.
The variations in this turbulence, which is often referred to as \emph{eddies}, is critical to understanding the evolution of the Southern Ocean under climate change.
But it's hard to get information about these eddies, because they occur on small scales in a large ocean basin that is poorly observed.
In addition, the observational record is quite short, which makes it more difficult to use these observations to study what controls variation in the eddy field.
For this reason, we take an eddy-permitting ocean model, and run it 50 times with the same forcing (but a slightly different initial state).
The chaotic nature of the turbulent ocean means that these model runs exhibit different evolutions.
We thus use these simulations to study which eddy processes are intrinsic (that is, a consequence of the chaotic nature of turbulence) and which are forced by the external forcing that is common to all experiments (such as wind forcing).
We conclude that the Southern Ocean eddy field is dominated by intrinsic chaotic processes; but that the forced variability responds to wind on particular timescales that are controlled by the mechanisms that generate ocean turbulence. 
\end{abstract}

@@

The Southern Ocean is unique in the global ocean; it is the one region without continents on its zonal boundaries, giving rise to the Antarctic Circumpolar Current (ACC) which flows eastward around the globe.
The ACC acts to connect the other major basins and thereby regulates climate and nutrients.
The Southern Ocean region is also a place where mid- and high-latitude ventilation of the oceans occurs, leading to carbon and heat uptake and controlling deep ocean stratification \citep{Rousselet2021, Morrison2022}.
However, the Southern Ocean is also poorly observed (compared with other ocean basins) and its unique properties mean that understanding the dynamics (with the aim of predicting future responses to climate change) need to be urgently constrained.

Another unique feature of the Southern Ocean is that it has a strong eddy field \citep{Fu2010}.
This strong eddy field has been suggested to be important in the Southern Ocean's response to change.
For example, the eddy saturation hypothesis \citep{Hallberg2006, Meredith-Hogg-2006, Munday2013, Constantinou2019} suggests that the role of eddies in facilitating vertical momentum transport acts to limit the response of ACC transport to changing winds.
A similar dynamics, known as eddy compensation, describes the role of eddies in moderating the effect of wind-driven change on the Southern Ocean overturning circulation \citep{Morrison2013a}.
Therefore, the response of fine scale transient motion in the Southern Ocean is likely important to characterising the dynamics of this region.

The strength of the Southern Ocean eddy field is usually characterised by extracting the kinetic energy of transient motions; referred to by oceanographers as eddy kinetic energy (EKE). 
It is important to highlight that EKE includes all transient motion, not just coherent vortices \citep{Martinez-Moreno2019}, and thus care needs to be taken in interpreting this metric.
Eddy kinetic energy has a complex relationship with the forces that drive the ocean circulation.
\citet{Meredith-Hogg-2006} found significant variations in the area-averaged eddy field in some regions, and argued for a 2-3 year lag between events in wind stress forcing and EKE anomalies.
\citet{Patara2016}, using a realistic high-resolution ocean model found that EKE does have a lagged response to wind stress anomalies, but that this relationship is variable around the Southern Ocean.
Idealised models over a wide range of parameter space \citep{Sinha2016} have highlighted that the timescale of the perturbation is critical in determining the EKE response, with shorter perturbations having a faster, Ekman-related response.
Thus, current knowledge suggests that there is a relationship between wind forcing and the Southern Ocean, but that the nature of this relationship needs to be clarified.

On longer timescales it has also been proposed that EKE has increased over recent decades \citep{Hogg2015, Martinez-Moreno2019, Martinez-Moreno2021-ncc}.
The robustness of this wind-EKE relationship in the Southern Ocean was recently investigated by \citet{Zhang2021}, who used crossover data from satellite observations \citep[as in][]{Hogg2015} to better estimate the EKE on regional scales.
When fine graining these calculations it was found that only a single region (30$^\circ$ in longitude) expressed a significant long-term trend in EKE.
This finding  suggests that previous characterisations of the response may have been dominated by a small number of regional events, calling into question the robustness of previous studies.

The dynamical importance of the Southern Ocean eddy field, and uncertainty over the robustness of its variability and trends, motivate a deeper investigation into the processes that control Southern Ocean eddies.
A key issue here is the extent to which the eddy field purely responds to external (atmospheric) forcing, versus the role of chaotic and intrinsic variability in determining eddy energy.
The fact that high-frequency eddy variability is random and chaotic is well-known, and even non-eddying ocean models can also produce (a small amount of) intrinsic variability via large-scale baroclinic instability \citep[e.g.][]{DeVerdiere1999}.
At longer timescales intrinsic variability can emerge from oceanic non-linearities under constant or seasonal forcing and persists under variable forcing \citep{Leroux2018}.
Such intrinsic variabilty has a random phase (that is, it is chaotic in character); it mostly emerges at mesoscale and can cascade toward interannual time scales and O(1000$\,$km) space scales \citep{Serazin-etal-2018}.
One of the goals of this work is characterise the spatiotemporal extent of chaotic, intrinsic, variability in determining  Southern Ocean EKE.

@@

The methodology employed in this study is derived from the probabilistic approach to ocean modelling outlined by \citet{Bessieres2017}.
We use output from the OCCIPUTensemble of 50 eddy-permitting global ocean--sea ice simulations, based on the ORCA025 implementation \citep[e.g.][]{Barnier2006} of the NEMO modelling system \citep{Madec2012}. 
The model grid has a 1/4$^\circ$ horizontal resolution and 75 geopotential levels. We employ the probabilistic ocean modelling approach outlined by \citet{Bessieres2017}: 
\begin{enumerate}
\item The 50 ensemble members are initialized in 1960 from a single-member 21-year spinup;
\item The ensemble spread is seeded by activating a stochastic perturbation \citep{Brankart-etal-2015} over one year (1960), after which the perturbation is terminated;
\item The 50 ensemble members are driven between 1960 and 2015 by the same realistic atmospheric forcing function based on the ERA-40 and ERA-Interim reanalyses (Drakkar Forcing Set DFS5.2; \citet{Dussin-etal-2016}).
\end{enumerate}
In these simulations the wind stress is computed without ocean current feedbacks, hence ensuring that the same momentum fluxes are applied to all members. 
We focus our analyses on the period 1980-2015, thus yielding an effective spinup duration of 41 years in each member.

@@

The sea level anomaly, $\eta_i'$, is calculated as the transient component of sea level, given by 
\begin{linenomath*}
\begin{equation}
\eta_i' = \eta_i - \overline{\eta_i},
\end{equation}
\end{linenomath*}
where $\overline{\cdot}$ represents the temporally filtered sea level \citep{Close2020}.
The sea level anomaly is detrended, and then used to calculate the eddy velocity field.
Surface eddy velocity in each ensemble member, $\mathbf{u}_i' = (u_i', v_i')$ is estimated from the detrended sea level anomaly via the geostrophic relation,
\begin{linenomath*}
\begin{equation}
u_i' = - \frac{g}{f} \frac{\partial \eta_i'}{\partial y} \quad \text{and} \quad v_i' = \frac{g}{f} \frac{\partial \eta_i'}{\partial x},
\end{equation}
\end{linenomath*}
where $g$ is the acceleration due to gravity and $f$ is the local Coriolis parameter.
Anomalous values of $\mathbf{u}_i'$ close to coastlines are removed.

@@

The eddy kinetic energy can be averaged over the $N$ ensemble members to give the ensemble mean EKE, written as
\begin{linenomath*}
\begin{equation}
\langle E_i \rangle = \frac{1}{N} \sum_{i=1}^N E_i.
\end{equation}
\end{linenomath*}
The argument can be made that, since each ensemble member is forced with identical atmospheric conditions, the forced EKE response is encapsulated by this ensemble mean quantity.
On the other hand, the intrinsic variability of EKE in each ensemble member is found by taking the difference from the ensemble mean for each member,
\begin{linenomath*}
\begin{equation}
E_i^* = E_i - \langle E_i \rangle,
\end{equation}
\end{linenomath*}
where $\cdot^*$ is used to indicate departure from the ensemble mean.
With these expressions in hand, we follow \citet{Leroux2018} to define the  time-variance of the ensemble-mean EKE,
\begin{linenomath*}
\begin{equation}
\sigma^2_{\langle E \rangle} = \frac{1}{T} \sum_{t=1}^T \left(\langle E_i \rangle -  \overline{\langle E_i \rangle}\right)^2,
\end{equation}
\end{linenomath*}
which represents the variance of the forced eddy response.
Analogously, the intrinsic variance emerges from the variance,
\begin{linenomath*}
\begin{equation}
\epsilon^2(t) = \frac{1}{N} \sum_{i=1}^N E_i^*(t)^2,
\end{equation}
\end{linenomath*}
indicating the spread of each member from the ensemble mean.
The fraction of intrinsic variance is then computed as the ratio of the intrinsic variance to the total variance,
\begin{linenomath*}
\begin{equation}
R_i =  \frac{\overline{\epsilon^2}}{\overline{\epsilon^2} + \sigma^2_{\langle E \rangle}}.
\end{equation}
\end{linenomath*}
When $R_i$ approaches unity, the system is dominated by intrinsic variability, and at the limit  of $R_i \to 0$ the system is solely responding to forced variability induced by atmospheric forcing.

@@

The intensity of the Southern Ocean eddy field is not uniform.
Snapshots of eddy kinetic energy (Fig.~\ref{Fig:1}a) show the occurrence of strong eddies which occur in the lee of subsurface topography and at the outlet from western boundary currents such as the Agulhas retroflection and Malvinas current.
The same patterns are evident in the ensemble and temporal mean of the eddy energy ($\langle\textrm{EKE}\rangle$; Fig.~\ref{Fig:1}b), although the signal of individual eddies is no longer apparent.
The strongest band of $\langle\textrm{EKE}\rangle$ approximately follows the path of the Antarctic Circumpolar Current, and $\langle\textrm{EKE}\rangle$  is weak south of 60$^\circ$S.
The patterns of $\langle\textrm{EKE}\rangle$  in this model broadly match the regional variations of $\langle\textrm{EKE}\rangle$  observed from satellite altimetry, albeit at slightly lower intensity, as expected in an eddy-permitting model \citep[e.g.][]{Kiss2020}.

@@

Although Southern Ocean EKE variability is strongly intrinsic, there remains a component of forced variability (red line in Fig.~\ref{Fig:2}a).
Previous studies have suggested that there is a strong contribution of wind stress forcing upon EKE, and we therefore compare the forced variability with the variations in wind stress averaged over the same circumpolar belt (black line in Fig.~\ref{Fig:2}a).
This comparison suggests a relationship in which wind stress leads variations in EKE, consistent with previously published results.
However, the time-lagged correlations between wind stress and EKE suggests that this relationship is complex. 
The intrinsically variable nature of Southern Ocean eddies means that for some ensemble members, there is no meaningful correlation between wind stress and eddies (grey lines in Fig~\ref{Fig:2}b).
On the other hand, ensemble member 5 (magenta line) has a clear (and significant; $T = 5.5$) correlation with a 4-month lag, while member 25 (orange line) is weakly correlated at 6 months, and significantly correlated ($T = 4.2$) at a 24-month lag.
These isolated examples highlight the differing behaviour of each ensemble member. 
The ensemble mean (red line in Fig~\ref{Fig:2}b) includes a significant correlation at $\sim$4 months and a second significant peak at $\sim$30 months.
Thus, two distinct timescales of response of the Southern Ocean eddy field to wind stress are present in this model.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure3}
\caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean. (a) Map showing Ensemble Mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Southeast Indian Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southwest Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (c) Regional analysis of the South Atlantic Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black. The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
\label{Fig:3}
\end{center}
\end{figure}

@@

In the Southeast Pacific Ocean (red box in Fig.~\ref{Fig:3}a) the situation is clearly different.
Here, the intrinsic variance fraction is larger than in the Southeast Indian Ocean ($R_i=0.78$) and the timescale of the variability is much longer; there is no significant response to wind stress variations which occur at sub-annual scales (Fig.~\ref{Fig:3}d).
The maximum values in the lag correlation occur over a broad band from 9-24 months in this region, without a single clear peak.
Thus, this region varies slowly and consistently to interannual variations in wind stress.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure4}
\caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean. (a) Map showing Ensemble Mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Central South Pacific Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southeast Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (e) Regional analysis of the Southwest Indian  Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black. The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
\label{Fig:4}
\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure5}
\caption{The spatial correlation of wind stress with $\langle\textrm{EKE}\rangle$ in (a) the Southeast Indian Ocean at 5-month lag; (b) the Southeast Indian Ocean at 30-month lag; (c) the Southwest Pacific ocean at 15-month lag and (d) the South Atlantic Ocean at 17-month lag.}
\label{Fig:5}
\end{center}
\end{figure}

>>>>

\documentclass[linenumbers]{agujournal2019}

\graphicspath{ {figures/} }
%\usepackage{lineno,layouts,microtype}

@@

%\linenumbers

@@

\newcommand{\mathbfit}[1]{\textbf{\textit{\textsf{#1}}}}
\usepackage{amsfonts, amssymb, amsmath}
%\usepackage[labelfont=bf]{caption}

@@

\authors{
Andrew McC. Hogg\affil{1}, Thierry Penduff\affil{2}, Sally E. Close\affil{2}, William K. Dewar\affil{3},\\Navid C. Constantinou\affil{1}, \quad and\quad Josu{\'e} Mart{\'i}nez-Moreno\affil{1}
}

@@

\begin{keypoints}
\item Variability in the Southern Ocean eddy field is dominated by chaotic, rather than forced, processes.
\item The forced component of the eddy kinetic energy variance is significantly correlated with the local wind stress input.
\item The eddy field lags the wind stress, with two clear timescales emerging: one at 4-6 months, which we attribute to baroclinic instability, and one at 2-3 years, which we attribute to the delayed effect of topographic steering.
\end{keypoints}

\begin{abstract}
Circulation in the Southern Ocean is unique.
The strong wind stress forcing and buoyancy fluxes, in concert with the lack of continental boundaries, conspire to drive the Antarctic Circumpolar Current replete with an intense eddy field.
The effect of Southern Ocean eddies on the ocean circulation is significant -- they modulate the momentum balance of the zonal flow, and the meridional transport of tracers and mass.
The strength of the eddy field is controlled by a combination of forcing (primarily thought to be wind stress) and intrinsic, or chaotic, variability associated with the turbulent flow field itself.
Here, we present results from an eddy-permitting ensemble of ocean model simulations to investigate the relative contribution of forced and intrinsic processes in governing the variability of Southern Ocean eddy kinetic energy.
We find that chaotic processes dominate the eddy field, even on longer (interannual) timescales.
Where correlations between the wind stress forcing and the eddy field exist, these interactions are dominated by two distinct timescales -- a fast baroclinic instability response; and a multi-year process owing to feedback between bathymetry and the mean flow.
These results suggest that understanding Southern Ocean eddy dynamics and its larger-scale impacts requires an ensemble approach to eliminate intrinsic variability, and therefore may not yield robust conclusions from observations alone.

\noindent \textbf{Plain language summary} \\
\noindent The Southern Ocean is the most turbulent part of the world's oceans.
The variation of this turbulence, which is often referred to as \emph{eddies}, is critical to understanding the evolution of the Southern Ocean under climate change.
But it's hard to get information about these eddies, because they occur on small scales in a large ocean basin that is poorly observed.
In addition, the observational record is quite short, which makes it more difficult to use these observations to study what controls variation in the eddy field.
For this reason, we take an eddy-permitting ocean model, and run it 50 times with the same forcing (but a slightly different initial state).
The chaotic nature of the turbulent ocean means that these model runs exhibit different evolutions.
We thus use these simulations to study which eddy processes are intrinsic (that is, a consequence of the chaotic nature of turbulence) and which are forced by the external factors that are common to all experiments (such as wind stress).
We conclude that the Southern Ocean eddy field is dominated by intrinsic chaotic processes; but that the forced variability responds to wind on particular timescales that are controlled by the mechanisms that generate ocean turbulence. 
\end{abstract}

@@

The Southern Ocean is unique in the global ocean; it is the one region without continents on its zonal boundaries, giving rise to the Antarctic Circumpolar Current (ACC) which flows eastward around the globe.
The ACC acts to connect the other major basins and thereby regulates climate and nutrients.
The Southern Ocean region is also a place where mid- and high-latitude ventilation of the oceans occurs, leading to carbon and heat uptake and controlling deep ocean stratification \citep{Rousselet2021, Morrison2022}.
However, the Southern Ocean is also poorly observed (compared with other ocean basins) and its unique properties mean that the dynamics of this region (with the aim of predicting future responses to climate change) need to be urgently constrained.

Another unique feature of the Southern Ocean is that it has a strong eddy field \citep{Fu2010}.
This eddy field has been suggested to be important in the Southern Ocean's response to change.
For example, the eddy saturation hypothesis \citep{Hallberg2006, Meredith-Hogg-2006, Munday2013, Constantinou2019} suggests that the role of eddies in facilitating vertical momentum transport acts to limit the response of ACC transport to changing winds.
A similar dynamics, known as eddy compensation, describes the role of eddies in moderating the effect of wind-driven change on the Southern Ocean overturning circulation \citep{Morrison2013a}.
Therefore, the response of fine scale transient motion in the Southern Ocean is likely important to characterising the dynamics of this region.

The strength of the Southern Ocean eddy field is usually characterised by extracting the kinetic energy of transient motions; referred to by oceanographers as eddy kinetic energy (EKE). 
It is important to highlight that EKE includes all transient motion, not just coherent vortices \citep{Martinez-Moreno2019}, and thus care needs to be taken in interpreting this metric.
Eddy kinetic energy has a complex relationship with the forces that drive the ocean circulation.
\citet{Meredith-Hogg-2006} found significant variations in the area-averaged eddy field in some regions, and argued for a 2-3 year lag between events in wind stress forcing and EKE anomalies.
\citet{Patara2016}, using a realistic high-resolution ocean model found that EKE does have a lagged response to wind stress anomalies, but that this relationship varies in strength around the Southern Ocean.
Idealised models over a wide range of parameter space \citep{Sinha2016} have highlighted that the timescale of the perturbation is critical in determining the EKE response, with shorter perturbations having a faster, Ekman-related response.
Thus, current knowledge suggests that there is a relationship between wind forcing and the Southern Ocean, but that the nature of this relationship needs to be clarified.

On longer timescales it has also been proposed that EKE has increased over recent decades \citep{Hogg2015, Martinez-Moreno2019, Martinez-Moreno2021-ncc}.
The robustness of this wind-EKE relationship in the Southern Ocean was recently investigated by \citet{Zhang2021}, who used crossover data from satellite observations \citep[as in][]{Hogg2015} to better estimate the EKE on regional scales.
When fine-graining these calculations it was found that only a single region (30$^\circ$ in longitude) expressed a significant long-term trend in EKE.
This finding  suggests that previous characterisations of the response may have been dominated by a small number of regional events, calling into question the robustness of previous studies.

The dynamical importance of the Southern Ocean eddy field, and uncertainty over the robustness of its variability and trends, motivate a deeper investigation into the processes that control Southern Ocean eddies.
A key issue here is the extent to which the eddy field purely responds to external (atmospheric) forcing, versus the role of chaotic and intrinsic variability in determining eddy energy.
The fact that high-frequency eddy variability is random and chaotic is well-known, and even non-eddying ocean models can produce (a small amount of) intrinsic variability via large-scale baroclinic instability \citep[e.g.][]{DeVerdiere1999}.
At longer timescales intrinsic variability can emerge from oceanic non-linearities under constant or seasonal forcing and persists under variable forcing \citep{Leroux2018}.
Such intrinsic variabilty has a random phase (that is, it is chaotic in character); it mostly emerges at mesoscale and can cascade toward interannual time scales and O(1000$\,$km) space scales \citep{Serazin-etal-2018}.
One of the goals of this work is characterise the spatiotemporal extent of chaotic, intrinsic, variability in determining  Southern Ocean EKE.

@@

The methodology employed in this study is derived from the probabilistic approach to ocean modelling outlined by \citet{Bessieres2017}.
We use output from the OCCIPUT ensemble of 50 eddy-permitting global ocean--sea ice simulations, based on the ORCA025 implementation \citep[e.g.][]{Barnier2006} of the NEMO modelling system \citep{Madec2012}. 
The model grid has a 1/4$^\circ$ horizontal resolution and 75 geopotential levels. 
The approach involves:
\begin{enumerate}
\item The 50 ensemble members are initialized in 1960 from a single-member 21-year spinup;
\item The ensemble spread is seeded by activating a stochastic perturbation \citep{Brankart-etal-2015} over one year (1960), after which the perturbation is terminated;
\item The 50 ensemble members are integrated from 1960 to 2015, driven by the same realistic atmospheric forcing function based on the ERA-40 and ERA-Interim reanalyses (Drakkar Forcing Set DFS5.2; \citet{Dussin-etal-2016}).
\end{enumerate}
In these simulations the wind stress is computed without ocean current feedbacks, hence ensuring that the same momentum fluxes are applied to all members. 
We focus our analyses on the period 1980-2015, thus yielding an effective spinup duration of 41 years in each member.

@@

The sea level anomaly, $\eta_i'$, is calculated as the transient component of sea level, given by 
\begin{linenomath*}
\begin{equation}
\eta_i' = \eta_i - \overline{\eta_i},
\end{equation}
\end{linenomath*}
where $\overline{\cdot}$ represents the temporally filtered, detrended sea level \citep{Close2020}.
The sea level anomaly is then used to calculate the eddy velocity field.
Surface eddy velocity in each ensemble member, $\mathbf{u}_i' = (u_i', v_i')$ is estimated from the detrended sea level anomaly via the geostrophic relation,
\begin{linenomath*}
\begin{equation}
u_i' = - \frac{g}{f} \frac{\partial \eta_i'}{\partial y} \quad \text{and} \quad v_i' = \frac{g}{f} \frac{\partial \eta_i'}{\partial x},
\end{equation}
\end{linenomath*}
where $g$ is the acceleration due to gravity and $f$ is the local Coriolis parameter.
Anomalous values of $\mathbf{u}_i'$ close to coastlines are removed.

@@

The eddy kinetic energy can be averaged over the $N$ ensemble members to give the ensemble mean EKE, written as
\begin{linenomath*}
\begin{equation}
\langle E_i \rangle = \frac{1}{N} \sum_{i=1}^N E_i.
\end{equation}
\end{linenomath*}
The argument can be made that, since each ensemble member is forced with identical atmospheric conditions, the forced EKE response is encapsulated by this ensemble mean quantity.
On the other hand, the intrinsic variability of EKE in each ensemble member is found by taking the difference from the ensemble mean for each member,
\begin{linenomath*}
\begin{equation}
E_i^* = E_i - \langle E_i \rangle,
\end{equation}
\end{linenomath*}
where $\cdot^*$ is used to indicate departure from the ensemble mean.
With these expressions in hand, we follow \citet{Leroux2018} to define the  time-variance of the ensemble-mean EKE,
\begin{linenomath*}
\begin{equation}
\sigma^2_{\langle E \rangle} = \frac{1}{T} \sum_{t=1}^T \left(\langle E_i \rangle -  \overline{\langle E_i \rangle}\right)^2,
\end{equation}
\end{linenomath*}
which represents the variance of the forced eddy response.
Analogously, the intrinsic variance emerges from the variance,
\begin{linenomath*}
\begin{equation}
\epsilon^2(t) = \frac{1}{N} \sum_{i=1}^N E_i^*(t)^2,
\end{equation}
\end{linenomath*}
indicating the spread of each member from the ensemble mean.
The fraction of intrinsic variance is then computed as the ratio of the intrinsic variance to the total variance,
\begin{linenomath*}
\begin{equation}
R_i =  \frac{\overline{\epsilon^2}}{\overline{\epsilon^2} + \sigma^2_{\langle E \rangle}}.
\end{equation}
\end{linenomath*}
When $R_i$ approaches unity, the system is dominated by intrinsic variability, while at the limit  of $R_i \to 0$ the system is solely responding to forced variability induced by atmospheric forcing.

@@

The intensity of the Southern Ocean eddy field is not uniform.
A snapshot of eddy kinetic energy from the model used here (Fig.~\ref{Fig:1}a) show the occurrence of strong eddies which occur in the lee of subsurface topography and at the outlet from western boundary currents such as the Agulhas retroflection and Malvinas current.
The same patterns are evident in the ensemble and temporal mean of the EKE ($\overline{\langle E_i \rangle}$; Fig.~\ref{Fig:1}b), although the signal of individual eddies is no longer apparent.
The strongest band of EKE approximately follows the path of the Antarctic Circumpolar Current, and EKE is weak south of 60$^\circ$S.
The patterns of EKE in this model broadly match the regional variations of EKE observed from satellite altimetry, albeit at slightly lower intensity, as expected in an eddy-permitting model \citep[e.g.][]{Kiss2020}.

@@

Although Southern Ocean EKE variability is strongly intrinsic, there remains a component of forced variability (red line in Fig.~\ref{Fig:2}a).
Previous studies have inferred that there is a strong contribution of wind stress forcing upon EKE, and we therefore compare the forced variability with the variations in wind stress averaged over the same circumpolar belt (black line in Fig.~\ref{Fig:2}a).
This comparison suggests a relationship in which wind stress leads variations in EKE, consistent with previously published results.
However, the time-lagged correlations between wind stress and EKE implies that this relationship is complex. 
The intrinsically variable nature of Southern Ocean eddies means that for some ensemble members, there is no meaningful correlation between wind stress and eddies (grey lines in Fig~\ref{Fig:2}b).
On the other hand, ensemble member 5 (magenta line) has a clear (and significant; $T = 5.5$) correlation with a 4-month lag, while member 25 (orange line) is weakly correlated at 6 months, and significantly correlated ($T = 4.2$) at a 24-month lag.
These isolated examples highlight the differing behaviour of each ensemble member. 
The ensemble mean (red line in Fig~\ref{Fig:2}b) includes a significant correlation at $\sim$4 months and a second significant peak at $\sim$30 months.
Thus, two distinct timescales of response of the Southern Ocean eddy field to wind stress are present in this model.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure3}
\caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean. (a) Map showing ensemble mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Southeast Indian Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southwest Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (e) Regional analysis of the South Atlantic Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black. The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
\label{Fig:3}
\end{center}
\end{figure}

@@

In the Southeast Pacific Ocean (red box in Fig.~\ref{Fig:3}a) the situation clearly differs.
Here, the intrinsic variance fraction is larger than in the Southeast Indian Ocean ($R_i=0.78$) and the timescale of the variability is much longer; there is no significant response to wind stress variations which occur at sub-annual scales (Fig.~\ref{Fig:3}d).
The maximum values in the lag correlation occur over a broad band from 9-24 months in this region, without a single clear peak.
Thus, this region varies slowly and consistently to interannual variations in wind stress.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure4}
\caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean. (a) Map showing ensemble mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Central South Pacific Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southeast Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (e) Regional analysis of the Southwest Indian  Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black. The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
\label{Fig:4}
\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure5}
\caption{The spatial correlation of wind stress with $\langle E_i \rangle$ in (a) the Southeast Indian Ocean at 5-month lag; (b) the Southeast Indian Ocean at 30-month lag; (c) the Southwest Pacific ocean at 15-month lag and (d) the South Atlantic Ocean at 17-month lag.}
\label{Fig:5}
\end{center}
\end{figure}

The heterogeneity in correlations between local wind and the ensemble mean EKE ($\langle E_i \rangle$) shows that, where forced variability in Southern Ocean EKE occurs, it can be partly explained by variations in wind stress.
However, these correlations are based purely on local wind stress -- averaged over the same area as the EKE statistics.
The existence of multi-year lags between the wind and the EKE suggests that local winds may not be the only source of energy for eddy generation; in particular, it is possible that energy could be advected a considerable distance downstream during this lag period.
To investigate this question we now take each of the regions outlined in Fig. \ref{Fig:3} and look at the spatial correlation between wind stress and the local ensemble mean EKE (Fig. \ref{Fig:5}).
To make this calculation, wind stress is first coarsened to a 4$^\circ \times $4$^\circ$ grid, and wind stress in each of those coarsened grid cells correlated with ensemble mean EKE at different lags.
In the Southeast Indian Ocean, Fig.~\ref{Fig:3}(c) shows correlation maxima at 5 months and 30 months; the spatial variation of this correlation is shown in Fig. \ref{Fig:5}(a,b) respectively.
These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong autocorrelations between wind stress along a line of latitude; nonetheless, the maximum correlation between wind stress and $\langle E_i \rangle$ occurs within the EKE-averaging region.
This correlation is lower in magnitude at 30 months (consistent with Fig.~\ref{Fig:3}c), but at both 5 and 30 month lags the correlation with wind upstream of the EKE-averaging region is not stronger than within the EKE-averaging region.
A similar result is found in the Southwest Pacific Ocean (Fig.~\ref{Fig:5}c); wind stress correlations are relatively uniform across the Pacific Ocean owing to the autocorrelation of winds, but the correlations are less circumpolar than the Southeast Indian Ocean.
Importantly, there is no suggestion of a strong correlation with wind stress upstream of the EKEaveraging region.
In the South Atlantic, the $\langle E_i \rangle$ is not strongly correlated with wind stress, either in the local region or elsewhere in the Southern Ocean (Fig.~\ref{Fig:5}d).
Thus, these spatial maps demonstrate that, where strong forced variability in the ensemble mean EKE exists, it is most strongly linked to local wind stress, with no suggestion of upstream or remote wind input playing a strong role.

\section{Discussion and Conclusions}
The simulations shown here advocate for a probabilistic approach to understanding the Southern Ocean eddy field.
The 50-member ensemble of eddy-permitting ocean-sea ice model simulations investigated here demonstrate that inference about the EKE response of a single ensemble member to variable forcing in a localised region is not robust, broadly consistent with the findings of \citet{Zhang2021}.
This point is clarified in Fig.~\ref{Fig:6} which shows a map of the intrinsic fraction of interannual variance, $R_i$, from eddy statistics interpolated onto a coarse (4$^\circ \times$4$^\circ$) grid, with eddy contributions filtered using a 12-month rolling mean.
Here, even at interannual timescales, the chaotic variance dominates over most of the band of elevated EKE in the Southern Ocean. 
Subpanels (b) and (c) confirm the predominance of intrinsic eddy variability at this scale, highlighting that at small scales we can place little reliability on the results from an individual ensemble member, or a single observation.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure7}
\caption{(a) The intrinsic variance fraction, $R_i$, averaged onto a  4$^\circ \times$4$^\circ$ grid and with a 12-month rolling mean; (b) amplitude of variability due to forced processes and (c) amplitude of variability due to intrinsic processes. }
\label{Fig:6}
\end{center}
\end{figure}
